Investigation of Limited Detection Schemes for Light Scattering of Optically Trapped Asymmetric Particles

### 2023-06-06 Latex files/Manuscript_Colloids.tex
cleaning up

\author[aff1]{Dan Maciver\corref{cor1}} 
\ead{Daniel.Maciver.2016@uni.strath.ac.uk}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}
\label{sec:Method}
\subsection{Orientation estimation from scattering measurements}
\label{sec:Bayes}

@@

We use the Brownian OT package developed by Fung~\textit{et~al} \cite{Vigilante2020Brownian_OT} to simulate the motion of an asymmetric dimer (Figure~\ref{fig:dimer}a) within an optical trap. Brownian OT combines MSTM \cite{Mishchenko1996MSTM} and ``Optical Tweezer Toolbox'' (\textit{ott}) \cite{Lenton2020} to simulate the motion of arbitrary
shaped sphere clusters. We simulate the motion of a dimer trapped in a highly focused Gaussian beam by calculating the optical forces imparted by the laser, and the Brownian force due to the surrounding fluid. MSTM provides the necessary T-matrix to compute the optical force via \textit{ott}. The Brownian force is found by computing the dimer's diffusion tensor according to the analytical solutions provided by Nir and Acrivos \cite{nir_acrivos_1973}. We simulated a silica dimer ($n = 1.45$) in a suspension of water ($n_{med} = 1.33$) over the course of $10 \ s$ with a simulation time step of $1 \times 10^{-3} \ s$.

@@

The Brownian OT software was used to simulate the motion of a trapped dimer ($a_1=1\,\mu{\rm m}$, $a_2=0.5\,\mu{\rm m}$) over the first $10$ seconds of entering the optical trap.  The initial orientation was assumed as strictly vertical (in line with the beam propagation direction). The dimer's position and orientation was recorded every $1\,{\rm ms}$ for using as a test dataset for our model.

>>>>

\author[aff1]{Daniel Maciver\corref{cor1}} 
\ead{Daniel.Maciver.2016@uni.strath.ac.uk}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}
\label{sec:Method}
\subsection{Orientation estimation from scattering measurements}
\label{sec:Bayes}

@@

We use the Brownian OT package developed by Fung~\textit{et~al} \cite{Vigilante2020Brownian_OT} to simulate the motion of an asymmetric dimer (Figure~\ref{fig:dimer}a) within an optical trap. Brownian OT combines MSTM \cite{Mishchenko1996MSTM} and ``Optical Tweezer Toolbox'' (\textit{ott}) \cite{Lenton2020} to simulate the motion of arbitrary
shaped sphere clusters. We simulate the motion of a dimer trapped in a highly focused Gaussian beam by calculating the optical forces imparted by the laser, and the Brownian force due to the surrounding fluid. MSTM provides the necessary T-matrix to compute the optical force via \textit{ott}. The Brownian force is found by computing the dimer's diffusion tensor according to the analytical solutions provided by Nir and Acrivos \cite{nir_acrivos_1973}. We simulated a polystyrene dimer ($n = 1.59$) in a suspension of water ($n_{med} = 1.33$) over the course of $1 \ s$ with a simulation time step of $1 \times 10^{-5} \ s$. We placed the dimer 4 microns below the trap focus at an angle $30^{\circ}$ from the horizontal, the resulting trajectory is shown below in Sec~\ref{sec:motion}. We chose these initial parameters because it demonstrates our model's performance in non steady state conditions.

@@

The Brownian OT software was used to simulate the motion of a trapped dimer ($a_1=1\,\mu{\rm m}$, $a_2=0.5\,\mu{\rm m}$) over the first $1$ seconds of entering the optical trap.  The initial orientation was set at $s = (0.923, 0.0, 0.385)$. The dimer's position and orientation was recorded every $10\,{\rm \mu s}$ for using as a test dataset for our model.

### 2023-06-06 Latex files/archive/Investigation into low light scattering.tex
cleaning up

	\section*{Introduction}
	Optical trapping has been a vital tool in the study of single molecule properties, the ability to deliver a stable and precise force vector has proved invaluable for studying biological groups in particular \cite{Biophysics_trapping}. Recent years there has been a growing interest in the study of colloid aggregation and growth; where the optical binding effect resulted in aggregation of particles around the trapping focus \cite{Colloids_and_tweezers}. Raman scattering techniques can be used to determine particle characteristics in a bulk or individual instance and have been applied to optical trapping methods to determine compositional information of the trapped entity \cite{Raman_Trapping,Raman_trapping_Biophysics}. However, the particle's dynamics in the trap can not be elucidated based purely on spectroscopy. For simple near spherical particles the motion can be largely attributed to Brownian motion which can be readily measured using a quadrant photo detector. It is not unusual however, that two microspheres to become attached to one another; in the presence of a focused Gaussian beam the microsphere dimer will reorient itself to align along the propagation axis of the beam. If the dimer is symmetrical then this reorientation motion is instantaneous, in the case of an asymmetrical dimer the alignment rapidly fluctuates about the propagation axis before eventually achieving an equilibrated orientation. Developing a method to model a dimer's motion within an optical trap based on information gathered in situ will prove useful for understanding the dynamics of more complexly shaped particle's that cannot be directly imaged.

	This has already been achieved with single microsphere using dynamic light scattering measurements of the trapping beam; where Bar-Ziv et al utilised dynamic light scattering to characterise the trap's stiffness and anisotropy based on the Brownian motion of a trapped silica microsphere \cite{Dynamic_trap_scattering}. They note that their method assumes that the silica scatters isotropically which allows them to place a single detection fibre at $75^\circ$ from the propagation axis. In the case where the trapped object scatters anisotropically - such as for an asymmetrical dimer - it is necessary to utilise multiple detection fibres to build a better picture of the trapped object's orientation based on the produced light scattering. However, for inverted microscope optical traps there is a significant engineering challenge of placing enough detection fibres at the correct angles within a close enough distance to the trapping focus to collect a clear signal. This means that any fibre based detection will have to rely on maximising the information provided by the light scattering signals collected at a limited number of detection fibres. Excluding the engineering challenge involved with ensuring proper coupling between the probe laser and the detection fibres, the primary concern is how much useful information can be extracted from the trapped particle.

	The experimental set up that this is based on is a inverted microscope optical trap, a suspension of micro particles are loaded onto a plastic cover slide. Onto the slide four optical fibres are stuck down; one fibre walks a 633 nm He-Ne laser onto the cover slip pointed directly at the trap focus, and the 3 remaining fibres are spaced equidistantly from the trap focus. The distance between each fibre and the trap focus is roughly $200\mu m$, with the exact angles between the particle and the trap focus being measured via the microscopes camera. The trapping laser is a 1064 nm NIR laser that is introduced via a 1.25 NA objective; to increase the trapping depth of the objective a lens of focal length 100 cm was added into the beam path to transform the profile entering the objective from parallel to converging, as advised by \cite{Long_distance_trap}'s paper.

@@

	\subsection*{Ultra-nest results}
	We first allowed ultra nest to traverse the parameter space while each angle was constrained to a predefined area. We assumed that the each fibre would be placed within a roughly $30^{\circ}$ range so that we get a sampling of the entire light scattering pattern, we didn't search further than $100^{\circ}$ as the signals would be to low to detect for a micron scale scatterer. The sampler ran until the divergence result was in the order of $10^1$.

@@

	\section*{Conclusion}
	We have developed a model for interpreting the dynamics of a trapped particle based purely on the light scattering pattern. The model can successfully predict the dimer's motion using its prior estimation to restrain the estimate in the physical space.

	Analysis of the parameter space for our choice of detection angles shows a strong preference for angles far from the $0^{\circ}$ suggesting a more accurate estimation can be achieved by considering back scattering signals. We hope to validate our model by collecting light scattering signals from a trapped dimer and testing it against the video and QPD signals generated from our result.

>>>>

	\section*{Introduction}
	Since their invention in the late 1980's, Optical Tweezers have found application in experiments ranging from single molecule biophysics~\cite{Wang 2021} to those that test the fundamental assumptions of Quantum Mechanics ~\cite{Duan 2013} thanks mainly to the ability of the tweezer to transduce and detect forces in the order of a few piconewton. Recent applications of the Optical Tweezers in metrological measurements ~\cite{Scott Waitukaitis} and colloidal aggregation ~\cite{Optical Binding} demand the tweezer to also be able to characterise  the trapped entity. To this end, chemical characterisation of the trapped entities has been achieved using spectroscopic techniques such as Raman Scattering ~\cite{P K Gupta} and dynamical characterisation has been achieved mainly by following the centre-of-mass brownian motion of the trapped entity using a Quadrant Photo Detector~\cite{Alexander Rohrbach}. While this technique has allowed for detection of linear motion of trapped entities  with sub-nanometre precision~\cite{Alexander Rohrbach} and  rotation~\cite{recent paper} of the centre-of-mass, there is a paucity of literature on measuring the orientation of trapped non-spherical particles till the recent attempt in ~\cite{New Zealand paper} where imaging was employed to study the orientation of trapped dimers and a resolution of () was achieved.

Possibility of integrating light scattering with optical trapping was demonstrated by Saffran et.al.,~\cite{Saffran} where a single-mode optical fibre was aligned to detect the scattered light from a trapped bead and it's brownian motion was studied. While this allowed for studying the dynamics, any information with regards structure of the trapped bead was precluded as the measurement was a single-angle scattering measurement.
In this work, we propose a novel Bayesian Inference based technique to interpret light scattering data detected in a scheme that expands on the technique in ~\cite{Saffran} to detect scattered light simultaneously at 3 angles as shown in Figure 1.

@@

	The issue with having a high signal error is that our model's prediction can be very far off from the correct answer and still be confident with it's results; fortunately our priori for the dimer's orientation can help to correct our estimate by limiting the probability in the physical space. We found that the inclusion of our priori estimate compared to a uniform priori imporved our results by around $20 \%$. We 
	\subsection*{Ultra-nest results}
	We first allowed ultra nest to traverse the parameter space while each angle was constrained to a predefined area. We assumed that the each fibre would be placed within a roughly $30^{\circ}$ range so that we get a sampling of the entire light scattering pattern, we didn't search further than $100^{\circ}$ as the signals would be to low to detect for a micron scale scatterer. The sampler ran until the divergence result was in the order of $10^1$.

@@

	\section*{Conclusion}
	We have developed a model for interpreting the dynamics of a trapped particle based purely on the light scattering pattern. Compared to a random selection of the particle's orientation we find that our model has a $150\%$ increase in it's accuracy. Even more interestingly, our model performs better under noisy signal conditions by allowing our estimate to self-correct itself, in the future we hope to remove the artifacts of the signal noise by combing multiple estimates using different detection angles. This can be achieved via the inclusion of additional signal detections, we refrained from collecting more signal point for two key reasons; firstly, we wanted to show the extent of the mathmatical model in the case of limited detection schemes, and secondly, we wanted to limit our model to what is possible in a real world experimental set up. Once we have a clearer understanding of the maximum limit of detection fibres that can be placed we can update our model to account for this and imporve the accuracy futher.

	Our simulations of asymetric dimers found that for large sphere ratios the dimer will prefer to be orientated against the beam propogation and will even move further from the trapping focus to invert itself before coming back to the laser focus. It is interesting that is only the case for dimers where the size ratio is greater than 1:2, understanding how the optical torque varies with size ratio can provide unique insight into the dynamics of non-spherical trapping targets.

	Overall the model developed can be applied to any characteristic that impacts the light scattering pattern produced by the trapped entity. The MSTM package is increadibly flexible and allows us to calculate the light scattering for a variety of micro partilces, so long as we can calculate the light scattering we can apply our model to help characterise the trapped model. We hope to extened this work for characterising continous processes such as nucleation within an optical trap.

### 2023-06-06 Latex files/archive/Manuscript_rev2-LL.tex
cleaning up

One reason we observe such large jumps in  orientation estimated from scattering signals is that there is no simple correlation between the 'distance in scattering space' between scattering signals from two different orientations, and their separation in orientation space : even a large change in orientation can involve a small change in scattering. Combining this fact with use of a uniform prior, indicating essentially no knowledge of how orientation should behave, there is no constraint on how much estimated orientation can change from time-step to time-step. To improve the estimation we can therefore use knowledge of the physical limitations of the object in the trap and its dynamics, imposing a more physically grounded prior,  accounting in this case for the fact that the motion of the dimer is limited due to the trap stiffness. Here the prior of the reference orientations $p(\hat{\bf n}_\alpha)$ was redefined at each time step according to the physical distance between the previous estimate $\hat{\bf n}_{est}(t-\Delta t)$ and each reference orientation $\hat{\bf n}_\alpha$, \textit{i.e.} taking into account the different likelihoods of the estimated orientation jumping between nearby or distant reference orientations:

>>>>

One reason we observe such large jumps in  orientation estimated from scattering signals is that there is no simple correlation between the 'distance in scattering space' between scattering signals from two different orientations, and their separation in orientation space : even a large change in orientation can involve a small change in scattering. Combining this fact with use of a uniform prior, indicating essentially no knowledge of how orientation should behave, there is no constraint on how much estimated orientation can change from timestep to timestep. To improve the estimation we can therefore use knowledge of the physical limitations of the object in the trap and its dynamics, imposing a more physically grounded prior,  accounting in this case for the fact that the motion of the dimer is limited due to the trap stiffness. Here the prior of the reference orientations $p(\hat{\bf n}_\alpha$ was redefined at each time step according to the physical distance between the previous estimate $\hat{\bf n}_{est}(t-\Delta t)$ and each reference orientation $\hat{\bf n}_\alpha$, \textit{i.e.} taking into account the different likelihoods of the estimated orientation jumping between nearby or distant reference orientations:

### 2023-06-06 Latex files/archive/Manuscript_rev3.tex
cleaning up

\usepackage{amssymb, amsthm}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{wrapfig}
\usepackage{geometry}
\usepackage{fancyref}
\usepackage{lineno}
\usepackage{color}
\usepackage{nomencl}
\makenomenclature
\renewcommand{\nomlabel}[1]{\hfil #1\hfil}

@@

While both \cite{Carvalho_2023} \cite{Watson_2023} demonstrate some ability to characterise trapped entities, \cite{Carvalho_2023} is perhaps best suited to characterise micron-sized particles and \cite{Watson_2023} talks about an experimental setup that is difficult to adopt and suffers from a low-bandwidth that might not be best suited for monitoring dynamics. A light scattering detection scheme built around an optical trap that is both easy to implement and has the advantage of high-bandwidth was demonstrated by Safran and co-workers in \cite{Bar-Ziv_1998}, where a single-mode optical fibre was aligned to detect the scattered light from a trapped bead and study its Brownian motion. While this provided dynamical information, structural information about the trapped bead was precluded as the measurement was obtained only at a single angle. Furthermore, the main drawback to a single fibre detection scheme is that it struggles to characterise isotropically scattering particles. This limits its application to biological matter as the internal structure of many cells makes them inherently isotropic scatterers \cite{Watson_2023}. In this work, we propose a scheme that expands on the technique in \cite{Bar-Ziv_1998} to detect scattered light simultaneously at a number of angles (Figure 1), combined with a novel Bayesian inference-based analysis technique to enable interpretation of the resulting multi-angle data as well as optimisation to provide maximal information from the signal.

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\begin{table}[h]
\begin{center}
\caption{\label{tab:A1}
%
Reference Orientations vector components$^*$}
\begin{tabular}{|c|c|c|c|}
\hline\hline
$\alpha$ & $\hat{\bf n}_{\alpha,\ x}$ &  $\hat{\bf n}_{\alpha,\ y}$ &  $\hat{\bf n}_{\alpha,\ z}$ \\
\hline
$1$  & $ 0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$2$  & $ 0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$3$  & $ 0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$4$  & $ 1.00000$ &  $ 0.00000$ & $ 0.00000$ \\
$5$  & $ 0.00000$ &  $ 1.00000$ & $ 0.00000$ \\
$6$  & $ 0.00000$ &  $ 0.00000$ & $ 1.00000$ \\
$7$  & $ 0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$8$  & $ 0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$9$  & $ 0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$10$ & $ 0.00000$ &  $ 0.00000$ & $-1.00000$ \\
$11$ & $ 0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$12$ & $ 0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$13$ & $ 0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$14$ & $ 0.00000$ &  $ -1.0000$ & $ 0.00000$ \\
$15$ & $ 0.29588$ &  $-0.29588$ & $-0.90825$ \\
$16$ & $ 0.90825$ &  $-0.29588$ & $-0.29588$ \\
$17$ & $ 0.29588$ &  $-0.90825$ & $-0.29588$ \\
$18$ & $-0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$19$ & $-0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$20$ & $-0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$21$ & $-1.00000$ &  $ 0.00000$ & $ 0.00000$ \\
$22$ & $-0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$23$ & $-0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$24$ & $-0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$25$ & $-0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$26$ & $-0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$27$ & $-0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$28$ & $-0.29588$ &  $-0.29588$ & $-0.90825$ \\
$28$ & $-0.90825$ &  $-0.29588$ & $-0.29588$ \\
$30$ & $-0.29588$ &  $-0.90825$ & $-0.29588$ \\
\hline\hline
\multicolumn{4}{l}{\small *Orientation vector points from centre of sphere 1 to centre of sphere 2.} \\
		\end{tabular}
	\end{center}
\label{sec:App1}
\end{table}

>>>>

\usepackage{amssymb, amsthm}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{wrapfig}
\usepackage{geometry}
\usepackage{fancyref}
\usepackage{lineno}
\usepackage{color}
\usepackage{nomencl}
\usepackage{array}
\usepackage{tabularx}
\makenomenclature
\renewcommand{\nomlabel}[1]{\hfil #1\hfil}

@@

While both \cite{Carvalho_2023} \cite{Watson_2023} demonstrate some ability to characterise trapped entities, \cite{Carvalho_2023} is perhaps best suited to characterise micron-sized particles and \cite{Watson_2023} talks about an experimental setup that is difficult to adopt and suffers from a low-bandwidth that might not be best suited for monitoring dynamics. A light scattering detection scheme built around an optical trap that is both easy to implement and has the advantage of high-bandwidth was demonstrated by Safran and co-workers in \cite{Bar-Ziv_1998}, where a single-mode optical fibre was aligned to detect the scattered light from a trapped bead and study its Brownian motion. While this provided dynamical information, structural information about the trapped bead was precluded as the measurement was obtained only at a single angle. Furthermore, the main drawback to a single fibre detection scheme is that it struggles to characterise anisotropically scattering particles. This limits its application to biological matter as the internal structure of many cells makes them inherently anisotropic scatterers \cite{Watson_2023}. In this work, we propose a scheme that expands on the technique in \cite{Bar-Ziv_1998} to detect scattered light simultaneously at a number of angles (Figure 1), combined with a novel Bayesian inference-based analysis technique to enable interpretation of the resulting multi-angle data as well as optimisation to provide maximal information from the signal.

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\begin{table}[h]
\begin{center}
\caption{\label{tab:A1}
%
Reference Orientations vector components$^*$}
\begin{tabularx}{0.65\textwidth}{
		| >{\centering\arraybackslash}X 
		| >{\centering\arraybackslash}X 
		| >{\centering\arraybackslash}X 
		| >{\centering\arraybackslash}X| }
\hline\hline
$\alpha$ & $\hat{\bf n}_{\alpha,\ x}$ & $\hat{\bf n}_{\alpha,\ y}$ &  $\hat{\bf n}_{\alpha,\ z}$ \\
\hline
$1$  & $ 0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$2$  & $ 0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$3$  & $ 0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$4$  & $ 1.00000$ &  $ 0.00000$ & $ 0.00000$ \\
$5$  & $ 0.00000$ &  $ 1.00000$ & $ 0.00000$ \\
$6$  & $ 0.00000$ &  $ 0.00000$ & $ 1.00000$ \\
$7$  & $ 0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$8$  & $ 0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$9$  & $ 0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$10$ & $ 0.00000$ &  $ 0.00000$ & $-1.00000$ \\
$11$ & $ 0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$12$ & $ 0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$13$ & $ 0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$14$ & $ 0.00000$ &  $ -1.0000$ & $ 0.00000$ \\
$15$ & $ 0.29588$ &  $-0.29588$ & $-0.90825$ \\
$16$ & $ 0.90825$ &  $-0.29588$ & $-0.29588$ \\
$17$ & $ 0.29588$ &  $-0.90825$ & $-0.29588$ \\
$18$ & $-0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$19$ & $-0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$20$ & $-0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$21$ & $-1.00000$ &  $ 0.00000$ & $ 0.00000$ \\
$22$ & $-0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$23$ & $-0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$24$ & $-0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$25$ & $-0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$26$ & $-0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$27$ & $-0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$28$ & $-0.29588$ &  $-0.29588$ & $-0.90825$ \\
$28$ & $-0.90825$ &  $-0.29588$ & $-0.29588$ \\
$30$ & $-0.29588$ &  $-0.90825$ & $-0.29588$ \\
\hline\hline
\multicolumn{4}{l}{\small *Orientation vector points from centre of sphere 1 to centre of sphere 2.} \\

\end{tabularx}
\end{center}
\label{sec:App1}
\end{table}
